---
title: "Learning Notes of CS231"
author: "Heyang Gong"
date: "`r Sys.Date()`"
output: 
  html_document: 
    number_sections: yes
    toc: yes
---

> tie: 神经网路等一切模型都是一个映射，把图片，视频变成一个高维空间中的向量。神经网路就是一个特征工程，一个降维过程。

```{r setup,eval=TRUE, echo=FALSE, warning=FALSE,message=FALSE}
knitr::opts_chunk$set(
  eval = FALSE,
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

This is a project of course notes for course CS231 by Standford.

```
1. quick start of learning this course
2. start from github official webisite http://cs231n.github.io/ 
3. 直接深入了解CNN。
4. Get to know Generative Adversarial Nets.


```

# Part I: Quick start


## Overview



CS231n focuses on one of the most important problems of visual recognition – image classification.

Convolutional Neural Networks (CNN) have become an important tool for object recognition.

> The philosophy

- Thorough and Detailed.
    - Understand how to write from scratch, debug and train convolutional neural networks.
- Practical.
    - Focus on practical techniques for training these networks at
scale, and on GPUs
- State of the art.
    - Most materials are new from research world in the past 1-3 years.
- Fun.
    - Some fun topics such as Image Captioning (using RNN)
    - Also DeepDream, NeuralStyle, etc.
    
课程的 Pre-requisite

- Proficiency in Python
- 数学基础
- 机器学习基础

课程的 Syllabus

课程大致包含 Course Intro, Image Classification, Loss function and Optimization,  Nerual networks, Convolutional Neural newtworks 等内容。


### python tutorial


```{r}
file.edit("scripts/quick-sort.py")
```

### Repos and best materials

http://cs231n.github.io/ 本课程资源官方资料网站


[subodh-malgonde/cs231n](https://github.com/subodh-malgonde/cs231n) 是非常好的一个 repo on github, 里面包含了，每次的作业.

http://study.163.com/course/courseMain.htm?courseId=1003223001 网易云课堂



## Start from the course site

http://cs231n.github.io/ 本课程资源官方资料网站, 从这个网站出发，一步步的学习。

由于没有双币信用卡，暂时放弃使用。

### assignment1

Image classification, KNN, SVM, Softmax, Neural network. I need to the following two things frist:

- https://github.com/subodh-malgonde/cs231n/tree/master/Assignments/assignment1, 直接研读前人的代码。
- 十分钟分别讲清楚 KNN， SVM， Softmax, Neural network 的优化目标函数和优化算法的实现。

```{r}
getwd()
file.edit("assignments/h1knn.py")
```


## CNN


http://cs231n.github.io/convolutional-networks/

depth, stride, zero-padding 三个CNN重要参数！

CNN是什么，有什么用，怎么用？


magic function in python?  %% timeit 


```{r}
getwd()
ls()
dir.create("scripts")
file.edit("scripts/cnn-minst.py")
```



 



## Questions

本章收集一些值得思考的问题，比如从现在到成为图像深度学习专家的最短路径是什么？



# Part II: 可视化

- [google 游乐场](http://playground.tensorflow.org)
- [卷积神经网路 MNIST 可视化](scs.ryerson.ca/~aharley/vis/conv/)


## gongfuzhou

随机梯度下降法，。。。

博弈算法 VS 贪婪算法

google or facebook 团队自动调参, 胡耀宗。

xuzongben... 

白板深度学习。

模拟退火的几乎最优条件。 

调节参数的一般过程，两种方法，从多到少，从少到多，最多10曾，一般每层不超过6个神经元。



# Part III: 生成式对抗网络

google "生成式对抗网络"

[到底什么是生成式对抗网络GAN?](https://zhuanlan.zhihu.com/p/26994666)